### 2022-01-18 src-latex/parts/10-introduction.tex
Reorganised end of section 5 to save space

Being active research topics, OCR and named entity recognition (NER) are still difficult tasks when applied to historical text documents.
OCR approaches used for modern documents are likely to struggle even on printed historical documents due multiple causes related to text readability (low resolution scans, inconsistent printing rules, artifacts, show-through), document complexity (intricate and versatile page layout, use of ancient fonts \& special glyphs) and the variability inherent to the huge diversity of historical sources.
\bertrand{J'ai tenté un premier refactoring, pas plus techniquement précis ceci dit.}
\nathalie{Phrases précedentes à reprendre avec les termes adéquats + ajouter une ref.}
On the other hand, NER approaches developed for modern texts suffer from the time gap between the contemporary entities and the entities mentioned in older texts and from the errors introduced into the text by the OCR step.\nathalie{ajouter une ref}

@@

In a recent work to locate potentially polluted urban soils \cite{bell2020automated}, trade directories were leveraged to identify and locate all the gas stations in the city of Providence during the XX\textsuperscript{th} century.
The proposed information extraction pipeline extract texts with OCR, identify directories entries and recognizes business type and address within each entry.
In the same way, we aim at producing structured spatio-temporal data from the Parisian trade directories.
These directories originate from several publishers, their content is organized following different indexing methods (by name, by activity or by address), printed in various layouts, use different fonts.
We therefore investigate several state-of-the-art OCR and NER approaches independently and in combination to assess their usability on the directories corpus.
The contributions of this article are the following:
% Contributions
\begin{enumerate}
    \item review state of the art regarding NER for historical documents (section 2)
    \item dataset (section 3)
    \item list usable techniques (more to evangelize the DAR community) (section 4)
    \item compare their performance under various training set sizes (thus annotation costs) and OCR noise levels (thus OCR choices/luck/availability) (sec. 5 and 6)
    \item suggest smart way to leverage side knowledge like lexicons (FIXME iif this works well, maybe a conclusion instead)
\end{enumerate}

>>>>

Being active research topics, OCR and named entity recognition (NER) are still difficult tasks when applied to historical text documents.
OCR approaches used for modern documents are likely to struggle even on printed historical documents due multiple causes related to text readability (low resolution scans, inconsistent printing rules, artifacts, show-through), document complexity (intricate and versatile page layout, use of ancient fonts \& special glyphs) and the variability inherent to the huge diversity of historical sources.
\bertrand{ajouter une ref.}
On the other hand, NER approaches developed for modern texts suffer from the time gap between the contemporary entities and the entities mentioned in older texts and from the errors introduced into the text by the OCR step.\nathalie{ajouter une ref}

@@

In a recent work to locate potentially polluted urban soils \cite{bell2020automated}, trade directories were leveraged to identify and locate all the gas stations in the city of Providence during the XX\textsuperscript{th} century.
The proposed information extraction pipeline extract texts with OCR, identify directories entries and recognizes business type and address within each entry.
In the same way, we aim at producing structured spatio-temporal data from the Parisian trade directories.
These directories originate from several publishers, their content is organized following different indexing methods (by name, by activity or by address), printed in various layouts, use different fonts.
We therefore investigate several state-of-the-art OCR and NER approaches independently and in combination to assess their usability on the directories corpus.
The contributions of this article are the following:
% Contributions
\begin{enumerate}
    \item review state of the art regarding NER for historical documents (section 2)
    \item dataset (section 3)
    \item list usable techniques (more to evangelize the DAR community) (section 4)
    \item compare their performance under various training set sizes (thus annotation costs) and OCR noise levels (thus OCR choices/luck/availability) (sec. 5 and 6)
    \item suggest smart way to leverage side knowledge like lexicons (FIXME iif this works well, maybe a conclusion instead) \nathalie{pas traité dans nos tests... à mettre en perspective}
\end{enumerate}

### 2022-01-18 src-latex/parts/50-xp-setup.tex
Reorganised end of section 5 to save space

\bertrand{Move after section Cases studies? }
\begin{itemize}
    \item NER quality: Precision, Recall, F1 score (idea: stick with standard spacy/sklearn metrics) \nathalie{Dans la plupart des articles que j'ai lus, c'est toujours une F-mesure qui est utilisée et parfois la précision et le rappel sont ajoutés.}
    \item OCR accuracy: outputs from standard tools (beware of unknown glyphs: do we need any special care?) \nathalie{Pour l'instant, j'ai croisé: CER, WER, Levenshtein et Jaccard. J'ai encore un état de l'art à lire sur le sujet: il y aura probablement d'autres mesures mentionnées.}

    \nathalie{Pour la partie Experiment 2: dans la litérature j'ai vu des courbes F-Mesure(CER) ou F-Mesure(WER) et des diagrammes avec F-Mesure calculée sur des sous-ensembles du corpus classés par score de Levenshtein.}
\end{itemize}

\subsection{Cases studies}
\subsubsection{Experiment 1: NER sensibility to the number of training samples}
The first experiment evaluates the performances of the three models on training sets of different sizes.
To do so, we split the gold reference into a training set, a development set, and a test set. The training set is then gradually reduced in size while maintaining the relative frequency of directories within.
The training and testing procedure is the same for the three models.

@@

\subsection{Experiment 2: NER in noisy OCRed texts}
This experiment aims to evaluate the impact of the OCR used on the quality of the NER results. To this end, we use directory entries whose text has been extracted, corrected and annotated manually (see Section 3). This reference text is aligned with the text produced on the same entries by Tesseract and PERO OCR. The named entities annotated in the reference text are then projected into the OCRed texts. To make sure that all training, development and test datasets contain the same annotations, only the entries for which the same number of annotations are found in the reference text and in the OCRised texts are kept. Finally, the reference text is divided into three datasets, using the same method as in Experiment 1. Two additional test files are generated with exactly the same entries as the test file produced from the reference text: one from the text produced by PERO OCR and one from that produced by Tesseract.

@@

%\subsection{Parameters for each method}

\subsection{OCR systems parameters}
\begin{itemize}
    \item original OCR
    \item Tesseract 4
    \item Pero
    \item other?
\end{itemize}

\subsection{Implementation details}
We use Spacy\mcite{spacy} for the CNN implementation
and Huggingface for the BERT 
tok2vec(words embeddings + encoding) + attention layer  +  transition-based model.

\paragraph{Huggingface CamemBERT}
CamemBERT + linear classifier as decision layer

>>>>

\subsection{NER sensibility to the number of training samples}
The first experiment evaluates the performances of the three models on training sets of different sizes.
To do so, we split the gold reference into a training set, a development set, and a test set. The training set is then gradually reduced in size while maintaining the relative frequency of directories within.
The training and testing procedure is the same for the three models.

@@

\subsection{NER in noisy OCRed texts}
The second experiment aims to evaluate the impact of the OCR used on the quality of the NER results. To this end, we use directory entries whose text has been extracted, corrected and annotated manually (see Section 3). This reference text is aligned with the text produced on the same entries by Tesseract and PERO OCR. The named entities annotated in the reference text are then projected into the OCRed texts. To make sure that all training, development and test datasets contain the same annotations, only the entries for which the same number of annotations are found in the reference text and in the OCRised texts are kept. Finally, the reference text is divided into three datasets, using the same method as in Experiment 1. Two additional test files are generated with exactly the same entries as the test file produced from the reference text: one from the text produced by PERO OCR and one from that produced by Tesseract.

@@

\subsection{Implementation details}

\subsubsection{OCR systems parameters}
\begin{itemize}
    \item original OCR
    \item Tesseract 4
    \item Pero
    \item other?
\end{itemize}

\subsubsection{Spacy}
We use Spacy\mcite{spacy} for the CNN implementation
and Huggingface for the BERT 
tok2vec(words embeddings + encoding) + attention layer  +  transition-based model.

\subsubsection{Huggingface CamemBERT}
\paragraph{Huggingface CamemBERT}
CamemBERT + linear classifier as decision layer
